### 2017-10-18 paper/sections/4_methodology.tex
paper: draft 1
Signed-off-by: Michael Sevilla <mikesevilla3@gmail.com>
paper: more eval organization
Signed-off-by: Michael Sevilla <mikesevilla3@gmail.com>

\section{Methodology: Global Namespace with Per-Subtree Consistency/Durability}
\label{sec:methodology-decoupled-namespaces}

@@

\begin{table}
\begin{tabular}{ r | l }
  Mechanism         & Description \\\hline
  RPCs              & round trip remote procedure calls \\
  Stream            & stream journal into object store \\
  Append Client Journal & events appended to in-memory journal \\
  Volatile Apply    & apply to metadata store in obj store \\
  Nonvolatile Apply & apply to metadata store in memory \\
  Local Persist     & journal saved to client's disk \\
  Global Persist    & journal saved in object store \\
\end{tabular}
\caption{The Cudele mechanisms are composed together to form consistency and
durability semantics.\label{table:mechanisms}} 
\end{table}

In this section we describe Cudele, our file system that lets users
assign consistency and durability semantics to subtrees in the global
namespace. A \textbf{mechanism} is an abstraction and basic building block for
constructing consistency and durability guarantees. Cudele exposes these
mechanisms and the user composes them together to construct
\textbf{policies}. These policies are assigned to subtrees and they dictate how
the file system should handle operations within that subtree.  Below, we
describe the mechanisms, the policies, and the API for assigning policies to
subtrees.

\subsection{The Cudele Mechanisms}
\label{sec:the-cudelesfs-mechanisms}

@@

\caption{Users can explore the consistency (C) and
durability (D) spectrums by composing Cudele mechanisms. 
\label{table:spectrum}}
\end{center}
\end{table}

>>>>

\section{Methodology: Global Namespace, Subtree Consistency/Durability}
\label{sec:methodology-decoupled-namespaces}

@@

\begin{table}
\begin{tabular}{ r | l }
  Mechanism         & Description \\\hline
  RPCs              & round trip remote procedure calls \\
  Stream            & stream journal into object store \\
  Append Client Journal & events appended to in-memory journal \\
  Volatile Apply    & apply to metadata store in obj store \\
  Nonvolatile Apply & apply to metadata store in memory \\
  Local Persist     & journal saved to client's disk \\
  Global Persist    & journal saved in object store \\
\end{tabular}
\caption{Mechanisms are composed together to form consistency and
durability semantics.\label{table:mechanisms}} 
\end{table}

In this section we describe Cudele, our API and framework that lets users
assign consistency and durability semantics to subtrees in the global
namespace. A \textbf{mechanism} is an abstraction and basic building block for
constructing consistency and durability guarantees. Cudele exposes these
mechanisms and the user composes them together to construct
\textbf{policies}. These policies are assigned to subtrees and they dictate how
the file system should handle operations within that subtree.  Below, we
describe the mechanisms, the policies, and the API for assigning policies to
subtrees.

\subsection{Mechanisms: Building Guarantees}
\label{sec:the-cudelesfs-mechanisms}

@@

\caption{Users can explore the consistency (C) and
durability (D) spectrum by composing Cudele mechanisms. 
\label{table:spectrum}}
\end{center}
\end{table}

### 2017-10-18 paper/sections/6_results.tex
paper: more eval organization
Signed-off-by: Michael Sevilla <mikesevilla3@gmail.com>

We evaluate our prototype, which we call Cudele, on two clusters: a 15 node
in-house cluster with 1 monitor server, 1 metadata server, 8 object storage
servers, and 8 clients (co-located with object servers); and a 34 node CloudLab
cluster with 1 monitor server, 1 metadata server, 3 object storage servers, and
up to 29 clients. For the in-house cluster, We need more object storage servers
and we have to co-locate clients on the same node because of resource
contention \footnote{The bandwidth to RADOS is only sufficient with 8 nodes on
this older hardware, which uses SSDs and nodes that are almost 10 years old.
The CloudLab cluster performs just as well with and without a highly
provisioned object storage server cluster.}. All daemons run as a single
process which is the default setting for Ceph. We develop on Ceph's Jewel
release, version 10.2.1, which was released in May 2016.

@@

% CITEME
Scientists use the file system to check the progress of jobs using
\texttt{ls}~\cite{CITEME}. The number of files or size of the files is
indicative of the progress. This practice is not too different from systems
that use the file system to manage the progress of jobs; Hadoop writes to
temporary files, renames them when complete, and creates a ``DONE" file to
indicate to the runtime that the task did not fail and should not be
re-scheduled on another node. In this scenario, Cudele users will not see the
progress of decoupled namespace since their updates are not globally visible.
To help scientists judge the progress of their jobs, Cudele has a ``namespace
sync" that sends batches of updates back to the global namespace at regular
intervals.

@@

% CITEME
The final uses case is reading large directories. At job completion, scientists
might use \texttt{ls} again to see the results. This causes great strain on the
file system as paths need to traversed and the entire directory, with all its
entries, must be transferred back to the client. Here we show how decoupling a
large namespace and materializing the view in memory on the client is faster
than doing RPCs for walks of the file system namespace.

>>>>

\begin{table}
\begin{tabular}{ r | l | l}
  Cluster  & Hardware               & Software \\\hline
  In-House & 15 nodes, 4 2GHz CPUs  & Ubuntu 12.04, 1 MON\\
           & 8GB RAM, SSD           & 1 MDS, 8 OSDs, 8 Clients\\
  CloudLab & 34 nodes, 16 2.4GHz CPUs & Ubuntu 14.04, 1 MON\\
           & 128GB RAM, SSD         & 1 MDS, 3 OSDs, 29 Clients
\end{tabular}
\caption{In-House used for microbenchmarks, CloudLab for Use Cases. MON is
monitor daemon, MDS is metadata server daemon, and OSDs are object storage
daemons.\label{table:clusters}} 
\end{table}

We evaluate our prototype on the two clusters in Table~\ref{table:clusters}.
Microbenchmarks were run on the in-house clusters while client scalability
tests were run on CloudLab. We only scale up to 29 clients because that is the
maximum capacity of a single metadata server. For the in-house cluster, we need
more object storage servers and we have to co-locate clients on the same node
because of resource contention \footnote{The bandwidth to RADOS is only
sufficient with 8 nodes on this older hardware, which uses SSDs and nodes that
are almost 10 years old.  The CloudLab cluster performs just as well with and
without a highly provisioned object storage server cluster.}. All daemons run
as a single process which is the default setting for Ceph. We develop on Ceph's
Jewel release, version 10.2.1, which was released in May 2016.

@@

% CITEME
Scientists use the file system to check the progress of jobs using
\texttt{ls}~\cite{CITEME}. The number of files or size of the files is
indicative of the progress. This practice is not too different from systems
that use the file system to manage the progress of jobs; Hadoop writes to
temporary files, renames them when complete, and creates a ``DONE" file to
indicate to the runtime that the task did not fail and should not be
re-scheduled on another node. In this scenario, Cudele users will not see the
progress of decoupled namespace since their updates are not globally visible.
To help scientists judge the progress of their jobs, Cudele clients have a
``namespace sync" that sends batches of updates back to the global namespace at
regular intervals.

% Does this implementation need to be described in the implementation?
FigureX shows the performance degradation of a single client writing updates to
a decoupled namespace and pausing to send updates to the metadata server. We
scale the namespace sync interval to show the trade-off of frequently pausing
or writing large logs of updates.  We use an idle core to log the updates and
to do the network transfer. The client only pauses to fork off a background
process, which is expensive as the address space needs to copied. The
alternative is to pause the client completely and write the update to disk but
since this implementation is limited by the speed of the disk, we choose the
memory-to-memory copy of the fork appraoch.`

To show the contention at the metadata server, we scale the number of
concurrent journal merge events in FigureX. The size of each journal is 100K
files, the maximum recommended directory size for CephFS. We also plot the cost
of RPCs with and without journaling.

@@

% CITEME
The final use case is reading large directories. At job completion, scientists
might use \texttt{ls} again to see the results. This causes great strain on the
file system as paths need to traversed and the entire directory, with all its
entries, must be transferred back to the client. Here we show how decoupling a
large namespace and materializing the view in memory on the client is faster
than doing RPCs for walks of the file system namespace.

FigureX shows how fast a client can materialize decoupled namespaces in memory.
This takes the on-disk file system metadata format and parses them into events
that can be manipulated and appended to. Again, we scale the number of up
